Central Slot Value Extraction from Internet for Wikipedia Entities

### 2013-10-29 paper/flairs27/content/abstract.tex

In this paper we will present the system design and algorithm adopted by the 
GatorDSR team, University of Florida to efficiently process TREC KBA 2013 --- 
SSF track. Here we will describe the system as well as the details 
the algorithms used to extract slot values for the given slot name. Scalability, efficiency, precision and recall are the major goals of this work, 
given the overly limited time limitation and available computational resources.

>>>>

In this paper we address extracting central knowledge from internet pertinent to entities in wikipedia, which is the most popular web-based, colaborative multilingual encyclopieda on the internet. This is comparable to Freebase in a query-driven manner. Our contributions are two fold, first we design a system to efficiently find central documents on the internet that contain direct information regarding a given wikipedia entity; second, we design a system to extract specific features of that entity from central documents which is refered to as slot filling. Our results demonstrate that the system is very efficient in the web scale nature of the problem: being highly memory and I/O efficient and that we can achieve high accuracy for given slot values.
